---
title: "Final Presentation"
author: "Laura Joslin"
date: '2023-05-10'
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # hide all the code
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## *Packages Used*


```{r, echo = TRUE}
library(tidyverse)
```
**I used this package for data manipulation.**


```{r, echo = TRUE}
library(skimr)
```
**I used this package to help manipulate my data frames, tibbles, data tables and vectors.**


```{r, echo = TRUE}
library(ggplot2)
```
**I used this package with creating the graphics.**



## Urban Park Ranger Animal Condition Response
. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .


* *This dataset provides information on animal help, relocation, and/or rescue requests conducted by the Urban Park Rangers.*

* *This data was found on data.gov*

. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .

**- There are 2,609 rows in this data set**

**- There are 22 columns, or variables in this data set**

**- Each row is a request completed by Urban Park Rangers**   
. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .


## Skimming the Data
```{r}
rawdata <- read_csv("https://data.cityofnewyork.us/resource/fuhs-xmg2.csv?$query=SELECT%0A%20%20%60date_and_time_of_initial%60%2C%0A%20%20%60date_and_time_of_ranger%60%2C%0A%20%20%60borough%60%2C%0A%20%20%60property%60%2C%0A%20%20%60location%60%2C%0A%20%20%60species_description%60%2C%0A%20%20%60call_source%60%2C%0A%20%20%60species_status%60%2C%0A%20%20%60animal_condition%60%2C%0A%20%20%60duration_of_response%60%2C%0A%20%20%60age%60%2C%0A%20%20%60animal_class%60%2C%0A%20%20%60_311sr_number%60%2C%0A%20%20%60final_ranger_action%60%2C%0A%20%20%60of_animals%60%2C%0A%20%20%60pep_response%60%2C%0A%20%20%60animal_monitored%60%2C%0A%20%20%60rehabilitator%60%2C%0A%20%20%60hours_spent_monitoring%60%2C%0A%20%20%60police_response%60%2C%0A%20%20%60esu_response%60%2C%0A%20%20%60acc_intake_number%60")
rawdata
```
## Wow that is a lot of data! 

*Lets narrow it down a bit to explore the critical information*

. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . .


***VARIBLES:***

* `of_animals`: Number of animals

* `animal_condition`: The animal's condition when discovered

* `final_ranger_action`: The park ranger's plan of action after discovering and observing the animal

* `animal_class`: The classification that the animal was identified into

## PLOT ONE: BAR GRAPH

```{r}
ggplot(rawdata, aes(x=animal_class, fill = of_animals)) + 
 geom_bar(size=2, shape=23, fill = "hot pink") +
theme(axis.text.x=element_text(angle = -90, hjust = 0)) +
 labs(
    title = "Classification of Animals conducted by Urban Park Rangers",
    x = "animal classifications",
    y = " number of animals",
   )
```

## PLOT TWO: Stacked Bar Chart

```{r}
ggplot(data = rawdata, aes(x = animal_condition, fill = type)) +
  geom_bar() + coord_flip() +
   labs(
    title = "Urban Park Ranger Actions In Response to Animal Condtins",
    x = "the condition that the animal were found in",
    y = " number of animals",
    fill = "park ranger actions"
  )
```











